%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{l3deliverable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage{graphicx}%
\usepackage{url}%
\usepackage{usecasedescription}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% See D1 for an example of how to integrate sub version revision
%% numbers into a LaTeX document.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Check these macro values for appropriateness for your own document.

\title{Prototyping Report}

\author{Ross Adam \\
        Andrew Gardner \\
        Nicole Kearns \\
        Mamas Nicolaou\\
	Asset Sarsengaliyev\\}

\date{29th November 2012}

\deliverableID{D4}
\project{PSD3 Group Exercise 1}
\team{V}
\version{1.0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\tableofcontents

\newpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Standard section for all documents

\section{Introduction}

\subsection{Identification}
Final report for the internship management project, containing the project plan, requirements specification, a report and demonstration of the prototype.

\subsection{Related Documentation}

PSD3 Group Exercise Description \url{http://fims.moodle.gla.ac.uk/file.php/128/coursework/psd3-ge-1-rev3278.pdf}\\

Deliverables Template \url{http://fims.moodle.gla.ac.uk/file.php/128/coursework/templates.zip}\\

PSD3 Course Notes \url{http://fims.moodle.gla.ac.uk/file.php/128/lecture-notes/notes-r3275.pdf}\\

\subsection{Purpose and Description of Document}
The purpose of this document is to give a detailed description of our
system prototype. This report includes a description of the scope and
design of the system and an evaluation of our prototype.
\subsection{Document Status and Schedule}

\begin{center}{
\begin{tabular}{|c|c|c|c|}
\hline \textbf{Date} &\textbf{ Change} & \textbf{Version} &\textbf{Author}\\ 
\hline  23/11/2012 & Began Draft & 0.1 & All\\
\hline 27/11/2012 & Finished Main Body & 0.2 & Ross Adam\\
\hline 28/11/2012 & Expanded Evaluation & 0.3 & Ross
Adam\\
\hline 28/11/2012 & Modified Section 2 and 3 & 0.4 & Andrew Gardner, Mamas Nicolaou\\
\hline 28/11/2012 & Finalised for Submission & 1.0 & Andrew Gardner, Mamas Nicolaou\\
\hline 29/11/2012 & \textbf{Final Submission Deadline} & 1.0 & Andrew Gardner, Mamas Nicolaou \\ 
\hline 
\end{tabular} }
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Objectives}

The objective of building the prototype was to manage the risks created by the remaining uncertainty left after the requirements gathering stages. If we did not build the prototype we may have progressed to the final development stages of the system without having fully clarified the final requirements. This could have led to increased development time and incomplete system features.\\
\\
The prototype was used as a demonstration tool to confirm with the clients that all major requirements had been included. Additionally it allowed us, as developers, to visualise the work flow within our system design. 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Prototype Scope and Design}

\subsection{Scope}

The scope of the prototype includes several essential elements:\\

\textbf{General:}\\

1. Allow separate logins for different types of users, specifically the subclasses Student, Course Co-ordinator and Company.\\
2. Allow each user to log out of the system. \\

\textbf{Student:}\\

1. Display a list of adverts.\\
2. Ability to select an advert to apply to from the displayed list.\\
3. Ability to notify Course Co-ordinator of successful application.\\

\textbf{Course Co-ordinator:}\\

1. Display a list of adverts that have been approved.\\
2. Display a list of adverts that are pending approval.\\
3. Ability to approve an advert from pending list.\\
 
\textbf{Company:}\\

1. Ability to submit an advert for approval.\\
2. Ability to edit an unapproved advert.\\

\subsection{Design}

Working with Bash Scripting significantly confines how a user can interact with the prototype system. Our interface uses textual commands to take input from the user. \\

The first thing a user sees is a login screen that prompts them for a username and then a password. Depending on the details provided the user will be taking to either the Student, Course Co-ordinator or Company screen. Each screen has unique options for the user to select. To allow ease of use for the users option selections are made with numbers that correspond to a command adjacent to them.  



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Evaluation}

Our evaluation was conducted with one of the clients: Rose English. We demonstrated the system by walking through the lifecycle of an advert from submission to eventual deletion.\\
\\
Firstly our demonstrator, Andrew Gardner, logged in as IBM to act as a company. He submitted a new advert using text inputs that restricted input to our pre-specified prompts. After the advert was submitted Andrew logged out of the company account and logged in as the Course Co-ordinator. From here he selected the option to look at adverts for approval and approved the IBM advert. Then he logged into a student account and accessed the list of approved adverts and applied for the IBM job. The Course Co-ordinator then deleted this advert after being notified of the student's successful application.\\
\\
After demonstrating our prototype we asked our client whether she felt that
our implementation satisfied her requirements. Rose said she
felt that all key aspects that she would want from the system were
included.\\
\\
The client demonstration confirmed that the functionality of our
program meets the client's requirements. Additionally it
provided insight into how the actual system will be implemented in the future.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
